Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2014-07-20 draft.tex
App. B: theta_1 <-> theta_2, and address Freds comments

The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \phi} = \frac{3}{8\pi} \sum_i \frac{J_{i}(q^2)}{\dd\Gamma/\dd q^2} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
\end{equation}
where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K^*}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
The $q^2$-differential decay width reads
\begin{equation}
    \frac{\dd\Gamma}{\dd q^2} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
\end{equation}
The angular functions read \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
\begin{aligned}
    f_{1s} & = \sin^2\theta_2 &
    f_{1c} & = \cos^2\theta_2 &
    f_{1i} & = \cos\theta_2\\
    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\phi &
    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\phi\\
    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\phi & & &
    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\phi\\
    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\phi & & &
    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\phi\\
    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\phi & & &
    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\phi\\
    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\phi & & &
    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\phi\,.
\end{aligned}
\end{equation}
We indicate contributions from the interference of S waves and P waves by an index \emph{i}. In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \phi) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $S_i(q^2) = J_i(q^2) / (\dd\Gamma/\dd q^2)$.\\

The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_1 - 42 \cos^2\theta_1\big) + \big(  45 \sin^2\theta_1 - 30 \cos^2\theta_1\big)\cos 2\theta_2}{64} \,,\\
    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_1 + 84 \cos^2\theta_1\big) + \big( -15 \sin^2\theta_1 + 60 \cos^2\theta_1\big)\cos 2\theta_2}{32} \,,\\
    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_1 - 30 \cos^2\theta_1\big) + \big(+135 \sin^2\theta_1 - 90 \cos^2\theta_1\big)\cos 2\theta_2}{64} \,,\\
    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_1 + 60 \cos^2\theta_1\big) + \big( -45 \sin^2\theta_1 +180 \cos^2\theta_1\big)\cos 2\theta_2}{32} \,,
\end{aligned}
\end{equation}
as well as
\begin{equation}
\begin{aligned}
    \hat{f}_{1sc}& = \frac{\big(21 + 15 \cos2\theta_2\big)\cos\theta_1}{16}               \,,&
    \hat{f}_{2sc}& = \frac{\big(15 + 45 \cos2\theta_2\big)\cos\theta_1}{16}               \,,\\
    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_1 -  6 \cos^2\theta_1\big)\cos\theta_2}{4} \,,&
    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_1 + 12 \cos^2\theta_1\big)\cos\theta_2}{2} \,,\\
    \hat{f}_{3}  & = \frac{75 \sin^2\theta_1 \sin^2\theta_2 \cos2\phi}{32}                \,,&
    \hat{f}_{9}  & = \frac{75 \sin^2\theta_1 \sin^2\theta_2 \sin2\phi}{32}                \,,\\
    \hat{f}_{4}  & = \frac{75 \sin 2\theta_1 \sin 2\theta_2 \cos \phi}{32}                \,,&
    \hat{f}_{4i} & = \frac{15 \sin  \theta_1 \sin 2\theta_2 \cos \phi}{8}                 \,,\\
    \hat{f}_{5}  & = \frac{15 \sin 2\theta_1 \sin  \theta_2 \cos \phi}{8}                 \,,&
    \hat{f}_{5i} & = \frac{3  \sin  \theta_1 \sin  \theta_2 \cos \phi}{2}                 \,,\\
    \hat{f}_{7}  & = \frac{15 \sin 2\theta_1 \sin  \theta_2 \sin \phi}{8}                 \,,&
    \hat{f}_{7i} & = \frac{3  \sin  \theta_1 \sin  \theta_2 \sin \phi}{2}                 \,,\\
    \hat{f}_{8}  & = \frac{75 \sin 2\theta_1 \sin 2\theta_2 \sin \phi}{32}                \,,&
    \hat{f}_{8i} & = \frac{15 \sin  \theta_1 \sin 2\theta_2 \sin \phi}{8}                 \,.
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \phi \hat{f}_i(\theta_1,\theta_2,\phi) P(q^2, \theta_1,\theta_2,\phi) = S_i(q^2)\,.
\end{equation}

>>>>

The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \theta_3} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\dd\Gamma/\dd q^2} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
\end{equation}
where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
The $q^2$-differential decay width reads
\begin{equation}
    \frac{\dd\Gamma}{\dd q^2} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
\end{equation}
The angular functions\footnote{%
    We consistently use the label "$i$" to denote angular function and observables that arise
    from interference between S-wave and P-wave amplitudes. Our convention is related to the convention
    of \cite{Bobeth:2012vn} through $f_{1i} \leftrightarrow f_{1sc}$, $f_{2i} \leftrightarrow f_{2sc}$.
} read \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
\begin{aligned}
    f_{1s} & = \sin^2\theta_2 &
    f_{1c} & = \cos^2\theta_2 &
    f_{1i} & = \cos\theta_2\\
    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\theta_3 &
    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 & & &
    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\theta_3\\
    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\theta_3 & & &
    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\theta_3\\
    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\theta_3 & & &
    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\theta_3\\
    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\theta_3 & & &
    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\,.
\end{aligned}
\end{equation}
We indicate contributions from the interference of S waves and P waves by an index \emph{i}. In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $S_k(q^2) \equiv J_k(q^2) / (\dd\Gamma/\dd q^2)$.\\

The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_2 - 42 \cos^2\theta_2\big) + \big(  45 \sin^2\theta_2 - 30 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_2 + 84 \cos^2\theta_2\big) + \big( -15 \sin^2\theta_2 + 60 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,\\
    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_2 - 30 \cos^2\theta_2\big) + \big(+135 \sin^2\theta_2 - 90 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_2 + 60 \cos^2\theta_2\big) + \big( -45 \sin^2\theta_2 +180 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,
\end{aligned}
\end{equation}
as well as
\begin{equation}
\begin{aligned}
    \hat{f}_{1i} & = \frac{\big(21 + 15 \cos1\theta_2\big)\cos\theta_2}{16}               \,,&
    \hat{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
    \hat{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,&
    \hat{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,,\\
    \hat{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
    \hat{f}_{4i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \cos \theta_3}{8}                 \,,\\
    \hat{f}_{5}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \cos \theta_3}{8}                 \,,&
    \hat{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
    \hat{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
    \hat{f}_{7i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \sin \theta_3}{2}                 \,,\\
    \hat{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
    \hat{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,.
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \dd\theta_1 \int_0^\pi\,\dd\theta_2\, \int_0^{2\pi}\dd \theta_3 \hat{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
\end{equation}
